Considering scale in multilayer animal social networks

### 2020-06-20 paper/manuscript.Rmd
fogo car ml cap

(ref:ml) Visualization of multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color. Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).

>>>>

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging). Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
